`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-19 inst/manuscript/manuscript.rmd
simplify get dependencies

```{r setting_up_r, echo = FALSE, message = FALSE}
library(flippant, quietly = TRUE)
library(magrittr, quietly = TRUE)
flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_split(regex = ",", omit_empty = TRUE) %>%
  unlist(use.names = FALSE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
  stringi::stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
  tail(n=length(.) - 1) %>%
  sort() %>%
  ( function(x){
    paste0(
      c(
        "`",
        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
        "` and `",
        tail(x, n = 1),
        "`"),
      collapse = "")} )

>>>>

```{r setting_up_r, echo = FALSE, message = FALSE}
library(flippant, quietly = TRUE)
library(magrittr, quietly = TRUE)
to_string <- function(x)
{
  paste(toString(head(x, -1)), "and", tail(x, 1))
}

# Copied from sig:::backquote
backquote <- function (x)
{
    x <- gsub("`", "\\\\`", x)
    paste0("`", x, "`")
}
flippant_dependencies <- "flippant" %>%
  tools::package_dependencies(installed.packages()) %>%
  extract2("flippant") %>%
  backquote %>%
  to_string
